The challenge and promise of software citation for credit, identification, discovery, and reuse

### 2016-07-02 SC-challenge.tex
shortened table entry

Standardize proper formats for citing software in publications &
The FORCE11 Software Citation Working Group is currently working to define and gain community acceptance for software citation principles, after which (starting in July 2016) a follow-on group will initiate implementation activities. \\

>>>>

Standardize proper formats for citing software in publications &
The FORCE11 Software Citation Working Group is defining, and gaining community acceptance for, software citation principles, after which a follow-on group will begin implementation efforts. \\
